Asynchronous vs Synchronous Selfish Learning

### 2018-10-15 Ordered Learning/ordered_learning.tex
New results toy scenario + start implementing dynamic scenarios

Two important implications are derived from the abovementioned mechanism: \emph{i)} the action-selection strategy of the learning algorithms are modified, \emph{ii)} the adversarial setting changes, so that the performance of every chosen action is potentially evaluated in a larger set of situations. According to the latter, a higher level of valuable knowledge is more likely to be provided to each arm. However, depending on the learning algorithm used, there can be other implications.

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_EG}
		\caption{Actions prob. (default)}\label{fig:actions_probability_EG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_OEG}
		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CEG}
		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CEG}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EG}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_EG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEG}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OEG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEG}
		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CEG}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_EG}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_OEG}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CEG}
		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CEG}
	\end{subfigure}
	\caption{Simulation results in $\varepsilon$-greedy (1,000 iterations)}
	\label{fig:e_greedy}
\end{figure*}

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_EXP3}
		\caption{Actions prob. (default)}\label{fig:actions_probability_EXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_OEXP3}
		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OEXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CEXP3}
		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CEXP3}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EXP3}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_EXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OEXP3}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OEXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEXP3}
		\caption{Temp. var.  (sync.  2)}\label{fig:temporal_individual_tpt_CEXP3}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_EXP3}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_OEXP3}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OEXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CEXP3}
		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CEXP3}
	\end{subfigure}
	\caption{Simulation results in EXP3 (1,000 iterations)}
	\label{fig:exp3}
\end{figure*}

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_UCB}
		\caption{Actions prob. (default)}\label{fig:actions_probability_UCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_OUCB}
		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OUCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CUCB}
		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CUCB}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_UCB}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_UCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OUCB}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OUCB}
	\end{subfigure}
		\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CUCB}
		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CUCB}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_UCB}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_UCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_OUCB}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OUCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CUCB}
		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CUCB}
	\end{subfigure}
	\caption{Simulation results in UCB (1,000 iterations)}
	\label{fig:ucb}
\end{figure*}

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_TS}
		\caption{Actions prob. (default)}\label{fig:actions_probability_TS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_OTS}
		\caption{Actions prob. (sync.)}\label{fig:actions_probability_OTS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CTS}
		\caption{Actions prob. (sync. 2)}\label{fig:actions_probability_CTS}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_TS}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_TS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_OTS}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_OTS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CTS}
		\caption{Temp. var.  (sync. 2)}\label{fig:temporal_individual_tpt_CTS}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_TS}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_TS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_OTS}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_OTS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CTS}
		\caption{Mean tpt. (sync. 2)}\label{fig:mean_tpt_CTS}
	\end{subfigure}
	\caption{Simulation results in Thompson sampling (1,000 iterations)}
	\label{fig:ts}
\end{figure*}

\section{Learning with penalties}
One promising possibility is to explore the effect of applying penalties to the reward, based on the transmit power or the saturation of a given channel (for that, we must know the number of users in each channel). Such penalties are not trivial to be derived, and when the problem becomes non-convex, the complexity increases. For that, we can provide some evidences about their usefulness when applying pure decentralized learning, but left its proper analysis as future work.

>>>>

Two important implications are derived from the abovementioned mechanism: \emph{i)} the action-selection strategies of the learning algorithms are modified, \emph{ii)} the adversarial setting changes, so that the performance of every chosen action is potentially evaluated in a larger set of situations. According to the latter, a higher level of valuable knowledge is more likely to be provided to each arm. However, depending on the learning algorithm used, there can be other implications.

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_EG}
		\caption{Actions prob. (default)}\label{fig:hist_actions_EG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CEG}
		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CEG}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EG}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_EG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEG}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CEG}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_EG}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EG}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CEG}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CEG}
	\end{subfigure}
	\caption{Simulation results in $\varepsilon$-greedy (1,000 iterations)}
	\label{fig:e_greedy}
\end{figure*}

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_EXP3}
		\caption{Actions prob. (default)}\label{fig:hist_actions_EXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CEXP3}
		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CEXP3}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_EXP3}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_EXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CEXP3}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CEXP3}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_EXP3}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_EXP3}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CEXP3}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CEXP3}
	\end{subfigure}
	\caption{Simulation results in EXP3 (1,000 iterations)}
	\label{fig:exp3}
\end{figure*}

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_UCB}
		\caption{Actions prob. (default)}\label{fig:hist_actions_UCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CUCB}
		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CUCB}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_UCB}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_UCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CUCB}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CUCB}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_UCB}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_UCB}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CUCB}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CUCB}
	\end{subfigure}
	\caption{Simulation results in UCB (1,000 iterations)}
	\label{fig:ucb}
\end{figure*}

@@

\begin{figure*}[h!]
	\centering
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_TS}
		\caption{Actions prob. (default)}\label{fig:hist_actions_TS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/actions_probability_CTS}
		\caption{Actions prob. (sync.)}\label{fig:hist_actions_CTS}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_TS}
		\caption{Temp. var.  (default)}\label{fig:temporal_individual_tpt_TS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/temporal_individual_tpt_CTS}
		\caption{Temp. var.  (sync.)}\label{fig:temporal_individual_tpt_CTS}
	\end{subfigure}\\
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_TS}
		\caption{Mean tpt. (default)}\label{fig:mean_tpt_TS}
	\end{subfigure}
	\begin{subfigure}[b]{.3\textwidth}
		\includegraphics[width=\textwidth]{images/mean_tpt_CTS}
		\caption{Mean tpt. (sync.)}\label{fig:mean_tpt_CTS}
	\end{subfigure}
	\caption{Simulation results in Thompson sampling (1,000 iterations)}
	\label{fig:ts}
\end{figure*}

\section{Learning with penalties (OPTIONAL)}
One promising possibility is to explore the effect of applying penalties to the reward, based on the transmit power or the saturation of a given channel (for that, we must know the number of users in each channel). Such penalties are not trivial to be derived, and when the problem becomes non-convex, the complexity increases. For that, we can provide some evidences about their usefulness when applying pure decentralized learning, but left its proper analysis as future work.
